% -------------------------
% Resume in Latex
% Author : Leopoldo Cuspinera
% OrignalTemplateAuthor : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\usepackage{ragged2e}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\huge
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\ind}{~~~~~}

\renewcommand{\baselinestretch}{1.4}



%-------------------------------------------
%%%%%%  Cover Letter variables  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\TO}{Hiring Manager}
\newcommand{\AT}{Blue Health Center}
\newcommand{\JOBTITLE}{Data Scientist}
\newcommand{\WHERE}{\href{https://www.linkedin.com/jobs/view/3816390946/?alternateChannel=search&refId=JdmEqCBvtVMhKfXXQGrGKQ\%3D\%3D&trackingId=zmDkJYpy66Sw7blhIcAFVg\%3D\%3D}{Linkedin}}


\begin{document}

% ----------HEADING-----------------
\section{Cover letter}
~\\
\Large Dear \TO,
\\
\justify{
\begin{quote} 
\large

\ind I recently noticed your open position for a  {\JOBTITLE} published on {\WHERE}. After reading its description I must say it seems like a great fit for me and hopefully, by the end of this cover letter, you’ll agree with me in considering I have the right set of skills and the determination required to fulfil this role.

\ind My profound interest in becoming a {\JOBTITLE} arose towards the end of my PhD in Theoretical Physics; I had decided to move away from academia to work in projects that had measurable, short-term, positive impact in society while still posing an interesting mathematical challenge.
Currently, at Camlin I have been given the opportunity to do so by analysing the data generated by the electrical network in the UK with the aim of profiling, understanding and forecasting the behaviour of different granularities of the grid.
Our analyses have become a major source of information and provide the visibility needed to optimise resources in the correct maintenance of the network by the different Distribution Network Operators. The findings driven by our team's projects have proven to be insightful and have driven both major and minor changes on both the technical and commercial fronts of our company.

%I decided to learn the right tools to become a Data Scientist and so I developed different projects that make use of different Machine Learning techniques (and programs and libraries like Python, Pandas, Scikit-learn, SQL, Jupyter, Tensorflow, Keras, Bokeh, Tableau and Wolfram Mathematica). 

\ind Previously, I also made analyses regarding customer experience generated while making appointments through automatised communications. My findings not only gave important data to stakeholders but the Tableau dashboards that were built became of such interest to customers that the access to their data through such dashboards became a data product itself.

\ind Finally, I would like to mention that in spite of how much I enjoy my current workplace, the activities I undertake and the general atmosphere within the company, 
I consider this job offer provides a place where my professional growth would be enhanced, within an experienced team that has clear objectives and poses a more interesting and adecquate challenge for me in the future.
I believe that {\AT} would suit my needs as a company and I am sure that I would be able to fulfil the expectations for this position. 

\ind In case you have any questions about my resume, please feel free to reach out over LinkedIn or email.

\begin{FlushRight}
Hope to hear from you soon,\\
Leopoldo Cuspinera.
\end{FlushRight}


\end{quote}
}
% 

%-------------------------------------------
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End: